%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Cloud Engineer} % Job title
    {Keepler} % Organization
    {Madrid, Spain} % Location
    {Apr. 2019 - Current} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Colaboration big data/ML projects using AWS}
        \item {Build sysops solutions using devops/scrum CI methodology (Ansible, Bash, Gitlab...)}
        \item {Design and implementation of AWS architectures using Terraform}
        \item {Develop custom serverless solutions using Python3 with boto3 and node (aws-sdk)} 
        \item {Python3/Ruby tooling development} 
        \item {Build A monitoring stack for the Big Data Cloud team using Grafana, influxdb, kibana, ES, Lua, Telegraf, Python...} 
        \item {Participate in projects using Event driven architecture, kafka openshift based} 
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Cloud Systems Developer} % Job title
    {OpenNebula Systems} % Organization
    {Madrid, Spain} % Location
    {Apr. 2017 - Apr.2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Driver developer and maintainer of some main drivers such as vCenter, EC2 or Azure. Bug fixing new features and designing and performing driver architecture rework}
        \item {Working with Linux Environment, administration, tooling and automation, using technologies like Jenkins, Ansible, Docker...}
        \item {In charge of vCenter onPrem environment}
        \item {Depeloping custom integrations between drivers and GUI using ruby and js}
        \item {Core development using c++ std11, bug fixing and features}
        \item {Developing of testing environment using Rspec}
        \item {Working with Hybrid cloud Architectures, installations, support and cloud deployments}
        \item {Consulting services: Networking (net appliances, linux bridges, cloud architectures...) Storage (NFS, ceph, disk and image management) Virtualization related (KVM, ESX, qemu...)}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Sofware Engineer} % Job title
    {Altran, I+D Aeronautics internship} % Organization
    {Madrid, Spain} % Location
    {Oct. 2016 - Apr. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Lead Developer of Mixed Reality project about computational fluid dynamics using Unity, Csharp, Oculus DK2 and Leap Motion}
        \item {Design of software architecture, develop algorithms and final product}
        \item {In charge of development environment, using Linux, Redmine and Git}
        \item {Git Manager of the project workflow}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Network technician} % Job title
    {Iberica Multimedia} % Organization
    {Malaga, Spain} % Location
    {Jul. 2013 - Aug. 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Local Area Network assembly, design and support of Starlite Festival 2013}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Network and Systems technician scholar} % Job title
    {Accenture} % Organization
    {Madrid, Spain} % Location
    {Mar. 2012 - Jul. 2012} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Based on Ciudad Financiera (Banco Santander)}
        \item {CPD maintenance}
        \item {Migrations}
        \item {Helpdesk}
      \end{cvitems}
    }

\end{cventries}
